---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library(explainr)
```

# explainr

### What is explainr?

**explainr** translates S3 objects into text using standard templates in a simple and convenient way. 

For help with the **explainr** R-package, there is a vignette available in the /vignettes folder.
  
# Installation

The package can be installed with

```r
devtools::install_github("hilaryparker/explainr")
```

After installation, the package can be loaded into R.

```r
library(explainr)
```

# Using explainr

The main function in the **explainr** package is `explain()`.  

```{r}
ptest <- prop.test(x = 500, n = 1008)
explain(ptest)
```

# Bug reports
Report bugs as issues on the [GitHub repository](https://github.com/hilaryparker/explainr)

# Inspiration
This project draws inspiration from the [CausalImpact package](https://github.com/google/CausalImpact).

# Contributors

* [Hilary Parker](https://github.com/hilaryparker)
* [David Robinson](https://github.com/dgrtwo)
* [Stephanie Hicks](https://github.com/stephaniehicks)
* [Roger Peng](https://github.com/rdpeng)
