---
title: "Introduction to explainr: Using Bioconductor Data"
author: "Hilary Parker, David Robinson, and Stephanie Hicks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to explainr: Using Bioconductor Data}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 5, fig.height = 5)
# options(digits=3)
```

This is a vignette for the **explainr** R package with the Bioconductor theme. We consider the Bottomly data set available on [Recount](http://bowtie-bio.sourceforge.net/recount/eset_tips.shtml). After finding the differentially expressed genes using two R/Bioconductor packages **voom** + **limma**, the object that is created is an `MArrayLM` object. We will apply the `explain()` function to the `MArrayLM` object which will explain the methods used for finding the differentially expressed genes and provide some basic summary plots.  


## Load libraries and RNA-Seq data
```{r, message=FALSE, warning=FALSE}
# Load libraries
library(Biobase)
library(biomaRt)
library(edgeR)
library(limma)
library(dplyr)
library(explainr)

# Load data
bottomly.local <- load(url("http://bowtie-bio.sourceforge.net/recount/ExpressionSets/bottomly_eset.RData"))
```

Create the RNA-Seq count table (ExpressionSet), phenotypic information, design matrix. 
```{r}
eset <- exprs(bottomly.eset)
keepMeID <- sapply(1:nrow(eset), function(x){ any(eset[x,] != 0) })
eset <- eset[keepMeID,]

pd <- phenoData(bottomly.eset)@data # sample information about the experiment 
design <- model.matrix(~pd$strain)
```

Calculate normalization factors to scale raw library sizes
```{r}
dge <- DGEList(counts = eset)
dge <- calcNormFactors(dge) 

# applies voom transformation to count data
v <- voom(dge, design = design) 
```

## Find the differentially expressed genes

Create the `MArrayLM` object using the R/Bioconductor `limma` package
```{r}
# Linear model for each gene and creates an MArrayLM object
fit <- lmFit(v, design)
fit <- eBayes(fit)
```

## `explain()` the analysis and results

```{r, results = 'asis'}
fit %>% explain(theme = "bioconductor")
```

