---
title: "Introduction to explainr"
author: "Hilary Parker, David Robinson, and Stephanie Hicks"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to explainr}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 5, fig.height = 5)
```

The `explainr` package turns R objects into easily understood plain English. For example, suppose we have a proportion test:

```{r ttest}
pt <- prop.test(2, 10, .5)
```

We could turn it into plain English with:

```{r explain1}
explain(pt)
```

In a knitr document, you might prefer to put `results = 'asis'`. For instance, in this next chunk, the output just looks like regular text:

```{r explain2, results = 'asis'}
explain(pt)
```

### Visual theme

You can change what theme you use. For instance, the `visual` theme, instead of just providing text, also displays images:

```{r lmdisplay, results = 'asis'}
m <- lm(mpg ~ wt, mtcars)

explain(m, "visual")
```
