---
name: prop.test
type: S3
---

```{r}
library(dplyr)
library(broom)
tidyx <- tidy(x)
onesamp <- TRUE  
if (length(x$estimate) == 2) onesamp <- FALSE
```

```{r stmt1} 
stmt1 <- paste0(
    "This was a ", if (onesamp) "one" else "two", 
    " sample proportion test of the null hypothesis that the ",
    if (onesamp) {
        paste0("true population proportion is equal to ", x$null.value, ".")
    } else {
        "two population proportions are equal."
    }
)
```

```{r stmt2}
if (x$p.value < 1 - attr(x$conf.int, "conf")) {
    if (onesamp == TRUE) {
        stmt2 <- paste0(
            "conclude that true population proportion is different than ",
            x$null.value, ".") 
        }
    if (onesamp == FALSE) {
        stmt2 <- paste0("conclude that two population proportions are not equal.") 
    }
    
} else {
    if (onesamp == TRUE) {
        stmt2 <- paste0(
            "cannot conclude that true population proportion is different than ",
            x$null.value, ".") 
        }
        
    if (onesamp == FALSE) {
        stmt2 <- paste0("cannot conclude that two population proportions are different from one another.") 
        }
}
```

```{r stmt3}

    if (onesamp == TRUE) {
        
        samps <- strsplit(x$data.name, ",") %>%
            unlist() %>%
            strsplit(split = " ") %>%
            unlist()
        
        x1 <- as.numeric(samps[1])
        n1 <- as.numeric(samps[4])
        
        
      stmt3 <- paste0("The observed number of events is ",
            prettyNum(x1, big.mark=","),
            ", out of a total sample size of ",
            prettyNum(n1, big.mark=","),
            '.'
        )    
    }

    if (onesamp == FALSE) {
        
        samps <- strsplit(x$data.name, "\\(" ) %>%
            unlist() %>%
            strsplit(split="\\)") %>%
            unlist() %>%
            strsplit(split=",") %>%
            unlist()
        
        x1 <- as.numeric(samps[2])
        x2 <- as.numeric(samps[3])
        n1 <- as.numeric(samps[5])
        n2 <- as.numeric(samps[6])  
        
    stmt3 <- paste0("The observed number of events in the first group is ",
            prettyNum(x1, big.mark=","), ", out of a total sample size of ",
            prettyNum(n1, big.mark=","), ". For the second group, the observed number of events is ",
            prettyNum(x2, big.mark=","), ", out of a total sample size of ",
            prettyNum(n2, big.mark=","), "."
        )
    }
```

`r cat(stmt1)` Using a significance level of `r 1 - attr(x$conf.int, "conf")`, we `r if (x$p.value < 1 - attr(x$conf.int, "conf")) cat("reject") else cat("do not reject")` the null hypothesis, and `r cat(stmt2)` `r cat(stmt3)`


The confidence interval for the true `r if (onesamp == TRUE) cat("population proportion") else cat("difference in population proportions")` is (`r tidyx$conf.low`, `r tidyx$conf.high`). That is, 95 times out of 100, this interval will contain the true `r if(onesamp == TRUE) cat("population proportion.") else cat("difference in population proportions.")`

The p-value for this test is `r x$p.value`. This, formally, is defined as the probability -- in the case that the null hypothesis is true -- of observing a `r if (onesamp == TRUE) cat("sample proportion") else cat("difference in sample proportions")` that is as or more extreme than the `r if (onesamp == TRUE) cat("sample proportion") else cat("difference in sample proportions")` from this data set. In this case, this is the probability -- in the case that the `r if (onesamp == TRUE) cat("population proportion") else cat("difference in population proportions")` is `r x$null.value`) were really true -- of observing a `r if (onesamp == TRUE) cat("sample proportion") else cat("difference in sample proportions")` that is greater than `r x$null.value + abs(x$estimate - x$null.value)` or less than `r x$null.value - abs(x$estimate - x$null.value)` assuming the null hypothesis (that . A smaller p-value can be used to reject the null hypothesis, and conclude that the data are not consistent with a true population proportion of `r x$null.value`. A common cutoff convention is a p-value of less than 0.05.
